{\RaggedRight
\begin{thebibliography}{9}
\addtolength{\leftmargin}{0.2in}
\setlength{\itemindent}{0.2in}
%Start Citations

  \bibitem{cattaneo88} G.Cattaneo, "The basic Hardware \& software to medium grain parallelism", 1988.
  
  \bibitem{bugnon97} E.Bugnion,S.Devine,K.Govil,M.Rosenblum, "Disco: Running Commodity Operating Systems on Scalable Multiprocessors", 1997.
  
  \bibitem{patterson88} D.Patterson,G.Gibson,K.H.Randy, "A Case for Redundant Arrays of Inexpensive Disks (RAID)", 1988.
  
  \bibitem{lowe04} David G. Lowe, "Distinctive Image Features from Scale-Invariant Keypoints", 2004.
  
  \bibitem{gamsa98} B.Gamsa,O.Krieger,J.Appavoo, M.Stumm, "Tornado: Maximizing Locality and Concurrency in a Shared Memory Multiprocessor Operating System", 1998.
  
  \bibitem{bershad95} B.Bershad,S.Savage,E.Siren,D.Becker,C.Chambers,S.Eggers, "Extensibility, Safety and Performance in the SPIN Operating System", 1995.
  
  \bibitem{hartig97}H.H\"{a}rtig,M.Hohmuth,J.Liedtke,S.Sch\"{o}nberg,J.Wolter, "The Performance of $\mu$-Kernel-Based Systems", 1997.
  
  \bibitem{rashid88} R.Rashid,A.Tevanian,M.Young,D.Golub,D.Black,J.Chew, "Machine Indipendent Virtual Memory Management for Paged Uniprocessor and Multiprocessor Architecture" 1988.
  
  \bibitem{appel91} A.Appel,K.Li, "Virtual Memory Primitives for User Programs", 1991.
  
  \bibitem{engler94} R.Engler,M.Kasshoek,J.O'Toole, "Exokernel:An Operating System Architecture for Application-Level Resource Management", 1994.
	\bibitem{kay89} J.Kay, P.Lauder, "A Fair Share Scheduler", 1989.
	\bibitem{waldspurger94} C.A.Waldspurger, W.E.Weihl, "Lottery Scheduling: Flexible Proportional-Share Resource Management", 1994.
	\bibitem{rosenblum92} M.Rosenblum, J.K.Osterhout, "The Design and Implementation of a Log-Structured File System", 1992.
	\bibitem{howard88} J.H.Howard, M.L.Kazar, S.G.Menees,D.A.Nichols,M.Satyanarayanan, R.N.Sidebotham, M.J.West, "Scale and Performance in a Distributed File System", 1988.
	\bibitem{kistler92} J.J.Kistler, M.Satyanarayanan, "Disconneted Operation in the Coda File System", 1992.
	\bibitem{anderson96} E.T.Anderson, M.D.Dahlin,J.M.Neefe,D.A.Patterson,D.S.Roselli,R.D.Wang, "Serverless Network File System", 1996.
	\bibitem{ghemawat03} S.Ghemawat,H.Gobioff,S.Leung, "The Google File System", 2003.
	\bibitem{thekkat94} A.Thekkat, M.Levy, D.Lazowska, "Separating Data And Control Transfer in Distributed Operating Systems", 1994.
	\bibitem{dahlin94} D.Dahlin, R.Wang, T.E.Anderson, D.A.Patterson, "Cooperative Caching: Using Remote Client Memory to Improve File System Performance", 1994.
	\bibitem{petersen97} K.Petersen,M.Spreitzer,D.B.Terry, Marvin.M.Theimer,A.J.Demers, "Flexible Update Propagation for Weakly Consistent Replication", 1997.
	\bibitem{gibson98} G.A.Gibson, D.F.Nagle, K.Amiri, J.Butler, F.W.Chang, H.Gobioff, C.Hardin, E.Riedel, D.Rochberg, J.Zelenka, "A Cost-Effective, High Bandwidth Storage Architecture", 1998.
\end{thebibliography}
}
